---
title       : Simple Data Product Project
subtitle    : Georgia High Schools - 2014 National Test Scores
author      : Kanti Chalasani
job         : Senior BI/Data Architect 
framework   : io2012        # {io2012, html5slides, shower, dzslides, revealjs,...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [bootstrap, quiz, shiny, interactive]   # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft, selfcontained}
ext_widgets : {rCharts: [libraries/nvd3]}
knit        : slidify::knit2slides


--- #montreal bg:url(http://goo.gl/cF6W2)


# Coursera Developing Data Products 

**2014 High School Scores - State of Georgia, US**
 

* **Kanti Chalasani**
* **January 23rd 2015**

---


## Project Introduction

As a parent I am always interested in the statistical facts about the schools in our school district as compared to  other schools within the State of Georgia. For this assignment, I chose to compare the National Test Scores performance and AP Course completions in 2014 for public schools within the State of Georgia, United States.

Data Source : [Georgia Deparment of Education (GaDOE)](http://www.gadoe.org/Curriculum-Instruction-and-Assessment/Curriculum-and-Instruction/Pages/SAT-and-ACT-Results.aspx)

Pre processed this data using other information on the same [website](http://www.gadoe.org/CCRPI/Pages/default.aspx) to prepare final data files that contain district information for this project. Data cleansing techniques were applied but have been kept out of score for this presentation.

---

## The Data

```{r echo=FALSE}
source("helpers.R")
write.csv(file="SATTop5.csv",SAT[1:5,])
write.csv(file="APTop10.csv",AP[1:10,])
write.csv(file="ACTTop10.csv",ACT[1:10,])
```

**SAT Data**

```{r echo=FALSE}
names(SAT)
```

**ACT Data**

```{r echo=FALSE}
names(ACT)
```

**AP Data**

```{r echo=FALSE}
names(AP)
```

---

## How is this website organized?

This website is organized into left and right panels.

* Left Panel - Data selection

  This panel allows you to choose the data level - State or District (in GA) or Atlanta Metro School Districts. This selection only applies to the first three tabs on the right panel.
  
* Right panel - Data Display

  This is organized into four tabs. First there tabs are one for each of the standardized assessments - SAT, AP and ACT respectively. 

  Fourth "School Comparison" tab  allows you to select the assessment type and any two high schools within the State of Georgia for comparison.


---

## Rankings Defined

* State.Rank - Rank assigned to this school within the State of Georgia.
* Selected.Schools.Rank - Rank assigned on the fly based on your current selection of the schools.

* Ranking Criteria - Highest to the lowest. 

SAT - Rank assigned based on SAT Combined Score.  

ACT - Rank assigned based on ACT Composite Score

AP - Rank assigned based on the percent of AP Course completions.


---

## Alanta Metro Public School Districts Definition

* Atlanta Public Schools
* Cherokee County
* Cobb County                                         
* DeKalb County
* Douglas County
* Forsyth County
* Fulton County
* Gwinnett County
* Buford City
* Decatur City
* Marietta City

---


AP 2014 Performance of Top 10 Schools in Georgia

```{r nvd3plot5, echo=F, results='asis', cache=F}
require(rCharts)
require(knitr)
library(reshape2)

APTop10<-read.csv("APTop10.csv")
h1 <- hPlot(x = "School", y = "AP_PASS_PCT", size = "Total.Exams.Taken", data = APTop10, type = "bubble")

h1$show('inline')

```

---


SAT 2014 Performance of Top 10 Schools in Georgia

```{r nvd3plot3, echo=F, results='asis', cache=F,fig.height=4,fig.width=5}
require(rCharts)
require(knitr)
##SATTop5<-SAT[1:5,]
SATTop5<-read.csv("SATTop5.csv")
r1 <- hPlot(Avg_Combined ~ School, 
            data = SATTop5, 
            color = 'School',
            type = 'bar'
)
r1$show('inline')

```


---

Interactive Report 

2014 Average Top Score by selected assessment type in Georgia

```{r opts.label ='shiny' }
library(shiny)
require(rCharts)
require(knitr)
slidifyUI(
  sidebarPanel(
    selectInput("ASSMT","Choose Assessment Type",choices =c("SAT","ACT","AP"),selected="SAT"),
    selectInput("Rnk","Choose School Rank 1 to 5",choices =c(1:5),selected="1")
    ),
    mainPanel(
      textOutput("ASSMT1"),
      hr(),
      textOutput("ASSMT")
      ##fluidRow(    dataTableOutput(outputId="sattable")          ),
      ##tags$div(id='nvd3plot',class='shiny-html-output nvd3 rChart')
    )
)

```

---

## Thank You

Thank You for visiting this website. 
